---
title: "Monthly Numbers"
date: "Last updated: 4/6/2021"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
---

```{css, echo=FALSE}
h1 {
  text-align: center;
}
```

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_knit$set(echo=FALSE, warning=FALSE, message=FALSE)
source("monthlyreport_functions.R")
data <- read.csv('February2021TrackingData.csv')
data$Date.Used <- strptime(as.character(data$Date.Used), "%m/%d/%Y")
tracking.data <-reformat_googlesheet(data)
tracking.data$date <- as.Date(tracking.data$date, format = "%Y-%m-%d")
```

Repository for CM/N Programs Monthly Tracking reports.

# February 2021

```{r February 2021 Enrollment, eval=FALSE, echo = FALSE, warning=FALSE, message=FALSE}
rows <- c("Media Meteorologists","Market Penetration (%)", "Local Television Stations", "Spanish-language Meteorologists", "Journalists Receiving CMN")
values <- c(968, 92, 483, 55, 702)
enrollment <- as.data.frame(cbind(rows, values))
names(enrollment) <- c(" ", "Enrollment")
library("formattable")
formattable(enrollment)
```


### Hits by Program
```{r February 2021 Hits by Type and Program, echo = FALSE, warning=FALSE, message=FALSE}
tracking.data.February2021 <- tracking.data[which(tracking.data$month=="February" & tracking.data$year=="2021"),]
#expanded view
library("tidyr")
expanded.hits.draft.February2021 <- hitsbyprogram(tracking.data.February2021)
expanded.hits.February2021 <- expanded.hits.draft.February2021[,c("source", "Twitter", "fb", "other",
                                  "online.article", "radio", "tv")]
#restrict data to CC, CM, CMN sources
expanded.hits.CMprograms.February2021 <- subset(expanded.hits.February2021, source=="CC"|source=="CM"|source=="CMN")
#aggregate hits according to nest program model
CMN.February2021 <- expanded.hits.CMprograms.February2021[3,2:7]
CM.February2021 <- CMN.February2021 + expanded.hits.CMprograms.February2021[2,2:7]
CC.February2021 <- CM.February2021 + expanded.hits.CMprograms.February2021[1,2:7]
aggregated.hits.CMprograms.February2021 <- rbind(CC.February2021, CM.February2021, CMN.February2021)
rownames(aggregated.hits.CMprograms.February2021) <- c("CC", "CM", "CMN")
#change column names
names(aggregated.hits.CMprograms.February2021) <- c("Twitter", "Facebook", "Other ",
                          "Online Articles", "Radio", "TV")
library("formattable")
aggregated.hits.formatted.February2021 <- formattable(aggregated.hits.CMprograms.February2021,
                                       align=c("l", "c", "c", "c", "c", "c", "c"),
                                       list(''))
aggregated.hits.formatted.February2021
```

### Comparison with Last Year
```{r February 2021 Last Year Comparison, echo = FALSE, warning=FALSE, message=FALSE}
tracking.data.February2021 <- tracking.data[which(tracking.data$month=="February" & tracking.data$year=="2021"),]
tracking.data.February2020 <- tracking.data[which(tracking.data$month=="February" & tracking.data$year=="2020"),]
previousYear(tracking.data.February2021, tracking.data.February2020)
```

### Top Releases

Most-used releases this month (including content released before this month).

```{r February 2021 Top Releases, warning=FALSE, echo = FALSE, warning=FALSE, message=FALSE}
rankedreleases.February2021 <- rankReleases(tracking.data.February2021)
top10releases.February2021 <-rankedreleases.February2021[c(1:10),]
names(top10releases.February2021) <- c("Release", "Social", "Stories", "TV", "Total")
top5releases.February2021 <-rankedreleases.February2021[c(1:5),]
names(top5releases.February2021) <- c("Release", "Social", "Stories", "TV", "Total")
library(DT)
datatable(top10releases.February2021, fillContainer=FALSE, options = list(scrollX="70px", scrollY="200px", pageLength = 5, dom = 'ftp'), rownames=FALSE)
```

### Hits by Region
```{r February 2021 Hits by Region, echo=FALSE, warning=FALSE, message=FALSE}
#compute hits by regions
month.hitsbyregion.February2021 <- hitsbyregion(tracking.data.February2021)
month.hitsbyregion.February2021
```

***

# January 2021

```{r January 2021 Enrollment, eval=FALSE, echo = FALSE, warning=FALSE, message=FALSE}
rows <- c("Media Meteorologists","Market Penetration (%)", "Local Television Stations", "Spanish-language Meteorologists", "Journalists Receiving CMN")
values <- c(968, 92, 483, 55, 702)
enrollment <- as.data.frame(cbind(rows, values))
names(enrollment) <- c(" ", "Enrollment")
library("formattable")
formattable(enrollment)
```


### Hits by Program
```{r January 2021 Hits by Type and Program, echo = FALSE, warning=FALSE, message=FALSE}
tracking.data.January2021 <- tracking.data[which(tracking.data$month=="January" & tracking.data$year=="2021"),]
#expanded view
library("tidyr")
expanded.hits.draft.January2021 <- hitsbyprogram(tracking.data.January2021)
expanded.hits.January2021 <- expanded.hits.draft.January2021[,c("source", "Twitter", "fb", "other",
                                  "online.article", "radio", "tv")]
#restrict data to CC, CM, CMN sources
expanded.hits.CMprograms.January2021 <- subset(expanded.hits.January2021, source=="CC"|source=="CM"|source=="CMN")
#aggregate hits according to nest program model
CMN.January2021 <- expanded.hits.CMprograms.January2021[3,2:7]
CM.January2021 <- CMN.January2021 + expanded.hits.CMprograms.January2021[2,2:7]
CC.January2021 <- CM.January2021 + expanded.hits.CMprograms.January2021[1,2:7]
aggregated.hits.CMprograms.January2021 <- rbind(CC.January2021, CM.January2021, CMN.January2021)
rownames(aggregated.hits.CMprograms.January2021) <- c("CC", "CM", "CMN")
#change column names
names(aggregated.hits.CMprograms.January2021) <- c("Twitter", "Facebook", "Other ",
                          "Online Articles", "Radio", "TV")
library("formattable")
aggregated.hits.formatted.January2021 <- formattable(aggregated.hits.CMprograms.January2021,
                                       align=c("l", "c", "c", "c", "c", "c", "c"),
                                       list(''))
aggregated.hits.formatted.January2021
```

### Comparison with Last Year
```{r January 2021 Last Year Comparison, echo = FALSE, warning=FALSE, message=FALSE}
tracking.data.January2021 <- tracking.data[which(tracking.data$month=="January" & tracking.data$year=="2021"),]
tracking.data.January2020 <- tracking.data[which(tracking.data$month=="January" & tracking.data$year=="2020"),]
previousYear(tracking.data.January2021, tracking.data.January2020)
```

### Top Releases

Most-used releases this month (including content released before this month).

```{r January 2021 Top Releases, warning=FALSE, echo = FALSE, warning=FALSE, message=FALSE}
rankedreleases.January2021 <- rankReleases(tracking.data.January2021)
top10releases.January2021 <-rankedreleases.January2021[c(1:10),]
names(top10releases.January2021) <- c("Release", "Social", "Stories", "TV", "Total")
top5releases.January2021 <-rankedreleases.January2021[c(1:5),]
names(top5releases.January2021) <- c("Release", "Social", "Stories", "TV", "Total")
library(DT)
datatable(top10releases.January2021, fillContainer=FALSE, options = list(scrollX="70px", scrollY="200px", pageLength = 5, dom = 'ftp'), rownames=FALSE)
```

### Hits by Region
```{r January 2021 Hits by Region, echo=FALSE, warning=FALSE, message=FALSE}
#compute hits by regions
month.hitsbyregion.January2021 <- hitsbyregion(tracking.data.January2021)
month.hitsbyregion.January2021
```

***

# December 2020

```{r December Enrollment, eval=FALSE, echo = FALSE, warning=FALSE, message=FALSE}
rows <- c("Media Meteorologists","Market Penetration (%)", "Local Television Stations", "Spanish-language Meteorologists", "Journalists Receiving CMN")
values <- c(968, 92, 483, 55, 702)
enrollment <- as.data.frame(cbind(rows, values))
names(enrollment) <- c(" ", "Enrollment")
library("formattable")
formattable(enrollment)
```


### Hits by Program
```{r December Hits by Type and Program, echo = FALSE, warning=FALSE, message=FALSE}
tracking.data.December2020 <- tracking.data[which(tracking.data$month=="December" & tracking.data$year=="2020"),]
#expanded view
library("tidyr")
expanded.hits.draft.December2020 <- hitsbyprogram(tracking.data.December2020)
expanded.hits.December2020 <- expanded.hits.draft.December2020[,c("source", "Twitter", "fb", "other",
                                  "online.article", "radio", "tv")]
#restrict data to CC, CM, CMN sources
expanded.hits.CMprograms.December2020 <- subset(expanded.hits.December2020, source=="CC"|source=="CM"|source=="CMN")
#aggregate hits according to nest program model
CMN.December2020 <- expanded.hits.CMprograms.December2020[3,2:7]
CM.December2020 <- CMN.December2020 + expanded.hits.CMprograms.December2020[2,2:7]
CC.December2020 <- CM.December2020 + expanded.hits.CMprograms.December2020[1,2:7]
aggregated.hits.CMprograms.December2020 <- rbind(CC.December2020, CM.December2020, CMN.December2020)
rownames(aggregated.hits.CMprograms.December2020) <- c("CC", "CM", "CMN")
#change column names
names(aggregated.hits.CMprograms.December2020) <- c("Twitter", "Facebook", "Other ",
                          "Online Articles", "Radio", "TV")
library("formattable")
aggregated.hits.formatted.December2020 <- formattable(aggregated.hits.CMprograms.December2020,
                                       align=c("l", "c", "c", "c", "c", "c", "c"),
                                       list(''))
aggregated.hits.formatted.December2020
```

### Comparison with Last Year
```{r December Last Year Comparison, echo = FALSE, warning=FALSE, message=FALSE}
tracking.data.December2020 <- tracking.data[which(tracking.data$month=="December" & tracking.data$year=="2020"),]
tracking.data.December2019 <- tracking.data[which(tracking.data$month=="December" & tracking.data$year=="2019"),]
previousYear(tracking.data.December2020, tracking.data.December2019)
```

### Top Releases

Most-used releases this month (including content released before this month).

```{r December Top Releases, warning=FALSE, echo = FALSE, warning=FALSE, message=FALSE}
rankedreleases.December2020 <- rankReleases(tracking.data.December2020)
top10releases.December2020 <-rankedreleases.December2020[c(1:10),]
names(top10releases.December2020) <- c("Release", "Social", "Stories", "TV", "Total")
top5releases.December2020 <-rankedreleases.December2020[c(1:5),]
names(top5releases.December2020) <- c("Release", "Social", "Stories", "TV", "Total")
library(DT)
datatable(top10releases.December2020, fillContainer=FALSE, options = list(scrollX="70px", scrollY="200px", pageLength = 5, dom = 'ftp'), rownames=FALSE)
```

### Hits by Region
```{r December Hits by Region, echo=FALSE, warning=FALSE, message=FALSE}
#compute hits by regions
month.hitsbyregion.December2020 <- hitsbyregion(tracking.data.December2020)
month.hitsbyregion.December2020
```

***

# November 2020

```{r November Enrollment, eval=FALSE, echo = FALSE, warning=FALSE, message=FALSE}
rows <- c("Media Meteorologists","Market Penetration (%)", "Local Television Stations", "Spanish-language Meteorologists", "Journalists Receiving CMN")
values <- c(968, 92, 483, 55, 702)
enrollment <- as.data.frame(cbind(rows, values))
names(enrollment) <- c(" ", "Enrollment")
library("formattable")
formattable(enrollment)
```


### Hits by Program
```{r November Hits by Type and Program, echo = FALSE, warning=FALSE, message=FALSE}
tracking.data.November2020 <- tracking.data[which(tracking.data$month=="November" & tracking.data$year=="2020"),]
#expanded view
library("tidyr")
expanded.hits.draft.November2020 <- hitsbyprogram(tracking.data.November2020)
expanded.hits.November2020 <- expanded.hits.draft.November2020[,c("source", "Twitter", "fb", "other",
                                  "online.article", "radio", "tv")]
#restrict data to CC, CM, CMN sources
expanded.hits.CMprograms.November2020 <- subset(expanded.hits.November2020, source=="CC"|source=="CM"|source=="CMN")
#aggregate hits according to nest program model
CMN.November2020 <- expanded.hits.CMprograms.November2020[3,2:7]
CM.November2020 <- CMN.November2020 + expanded.hits.CMprograms.November2020[2,2:7]
CC.November2020 <- CM.November2020 + expanded.hits.CMprograms.November2020[1,2:7]
aggregated.hits.CMprograms.November2020 <- rbind(CC.November2020, CM.November2020, CMN.November2020)
rownames(aggregated.hits.CMprograms.November2020) <- c("CC", "CM", "CMN")
#change column names
names(aggregated.hits.CMprograms.November2020) <- c("Twitter", "Facebook", "Other ",
                          "Online Articles", "Radio", "TV")
library("formattable")
aggregated.hits.formatted.November2020 <- formattable(aggregated.hits.CMprograms.November2020,
                                       align=c("l", "c", "c", "c", "c", "c", "c"),
                                       list(''))
aggregated.hits.formatted.November2020
```

### Comparison with Last Year
```{r November Last Year Comparison, echo = FALSE, warning=FALSE, message=FALSE}
tracking.data.November2020 <- tracking.data[which(tracking.data$month=="November" & tracking.data$year=="2020"),]
tracking.data.November2019 <- tracking.data[which(tracking.data$month=="November" & tracking.data$year=="2019"),]
previousYear(tracking.data.November2020, tracking.data.November2019)
```

### Top Releases

Most-used releases this month (including content released before this month).

```{r November Top Releases, warning=FALSE, echo = FALSE, warning=FALSE, message=FALSE}
rankedreleases.November2020 <- rankReleases(tracking.data.November2020)
top10releases.November2020 <-rankedreleases.November2020[c(1:10),]
names(top10releases.November2020) <- c("Release", "Social", "Stories", "TV", "Total")
top5releases.November2020 <-rankedreleases.November2020[c(1:5),]
names(top5releases.November2020) <- c("Release", "Social", "Stories", "TV", "Total")
library(DT)
datatable(top10releases.November2020, fillContainer=FALSE, options = list(scrollX="70px", scrollY="200px", pageLength = 5, dom = 'ftp'), rownames=FALSE)
```

### Hits by Region
```{r November Hits by Region, echo=FALSE, warning=FALSE, message=FALSE}
#compute hits by regions
month.hitsbyregion.November2020 <- hitsbyregion(tracking.data.November2020)
month.hitsbyregion.November2020
```

***

# October 2020

```{r October Enrollment, eval=FALSE, echo = FALSE, warning=FALSE, message=FALSE}
rows <- c("Media Meteorologists","Market Penetration (%)", "Local Television Stations", "Spanish-language Meteorologists", "Journalists Receiving CMN")
values <- c(968, 92, 483, 55, 702)
enrollment <- as.data.frame(cbind(rows, values))
names(enrollment) <- c(" ", "Enrollment")
library("formattable")
formattable(enrollment)
```


### Hits by Program
```{r October Hits by Type and Program, echo = FALSE, warning=FALSE, message=FALSE}
tracking.data.October2020 <- tracking.data[which(tracking.data$month=="October" & tracking.data$year=="2020"),]
#expanded view
library("tidyr")
expanded.hits.draft.October2020 <- hitsbyprogram(tracking.data.October2020)
expanded.hits.October2020 <- expanded.hits.draft.October2020[,c("source", "Twitter", "fb", "other",
                                  "online.article", "radio", "tv")]
#restrict data to CC, CM, CMN sources
expanded.hits.CMprograms.October2020 <- subset(expanded.hits.October2020, source=="CC"|source=="CM"|source=="CMN")
#aggregate hits according to nest program model
CMN.October2020 <- expanded.hits.CMprograms.October2020[3,2:7]
CM.October2020 <- CMN.October2020 + expanded.hits.CMprograms.October2020[2,2:7]
CC.October2020 <- CM.October2020 + expanded.hits.CMprograms.October2020[1,2:7]
aggregated.hits.CMprograms.October2020 <- rbind(CC.October2020, CM.October2020, CMN.October2020)
rownames(aggregated.hits.CMprograms.October2020) <- c("CC", "CM", "CMN")
#change column names
names(aggregated.hits.CMprograms.October2020) <- c("Twitter", "Facebook", "Other ",
                          "Online Articles", "Radio", "TV")
library("formattable")
aggregated.hits.formatted.October2020 <- formattable(aggregated.hits.CMprograms.October2020,
                                       align=c("l", "c", "c", "c", "c", "c", "c"),
                                       list(''))
aggregated.hits.formatted.October2020
```

### Comparison with Last Year
```{r October Last Year Comparison, echo = FALSE, warning=FALSE, message=FALSE}
tracking.data.October2020 <- tracking.data[which(tracking.data$month=="October" & tracking.data$year=="2020"),]
tracking.data.October2019 <- tracking.data[which(tracking.data$month=="October" & tracking.data$year=="2019"),]
previousYear(tracking.data.October2020, tracking.data.October2019)
```

### Top Releases

Most-used releases this month (including content released before this month).

```{r October Top Releases, warning=FALSE, echo = FALSE, warning=FALSE, message=FALSE}
rankedreleases.October2020 <- rankReleases(tracking.data.October2020)
top10releases.October2020 <-rankedreleases.October2020[c(1:10),]
names(top10releases.October2020) <- c("Release", "Social", "Stories", "TV", "Total")
top5releases.October2020 <-rankedreleases.October2020[c(1:5),]
names(top5releases.October2020) <- c("Release", "Social", "Stories", "TV", "Total")
library(DT)
datatable(top10releases.October2020, fillContainer=FALSE, options = list(scrollX="70px", scrollY="200px", pageLength = 5, dom = 'ftp'), rownames=FALSE)
```

### Hits by Region
```{r October Hits by Region, echo=FALSE, warning=FALSE, message=FALSE}
#compute hits by regions
month.hitsbyregion.October2020 <- hitsbyregion(tracking.data.October2020)
month.hitsbyregion.October2020
```

***

# September 2020

```{r September setup, echo = FALSE, warning=FALSE, message=FALSE}
tracking.data.September2020 <- tracking.data[which(tracking.data$month=="September" & tracking.data$year=="2020"),]
```


### Hits by Program
```{r September Hits by Type and Program, echo = FALSE, warning=FALSE, message=FALSE}
#expanded view
library("tidyr")
expanded.hits.draft.September2020 <- hitsbyprogram(tracking.data.September2020)
expanded.hits.September2020 <- expanded.hits.draft.September2020[,c("source", "Twitter", "fb", "other",
                                  "online.article", "radio", "tv")]
#restrict data to CC, CM, CMN sources
expanded.hits.CMprograms.September2020 <- subset(expanded.hits.September2020, source=="CC"|source=="CM"|source=="CMN"|source=="Total")
#aggregate hits according to nest program model
CMN.September2020 <- expanded.hits.CMprograms.September2020[3,2:7]
CM.September2020 <- CMN.September2020 + expanded.hits.CMprograms.September2020[2,2:7]
CC.September2020 <- CM.September2020 + expanded.hits.CMprograms.September2020[1,2:7]
aggregated.hits.CMprograms.September2020 <- rbind(CC.September2020, CM.September2020, CMN.September2020)
rownames(aggregated.hits.CMprograms.September2020) <- c("CC", "CM", "CMN")
#change column names
names(aggregated.hits.CMprograms.September2020) <- c("Twitter", "Facebook", "Other ",
                          "Online Articles", "Radio", "TV")
library("formattable")
aggregated.hits.formatted.September2020 <- formattable(aggregated.hits.CMprograms.September2020,
                                       align=c("l", "c", "c", "c", "c", "c", "c"),
                                       list(''))
aggregated.hits.formatted.September2020
```

### Comparison with Last Year
```{r September Last Year Comparison, echo = FALSE, warning=FALSE, message=FALSE}
tracking.data.September2020 <- tracking.data[which(tracking.data$month=="September" & tracking.data$year=="2020"),]
tracking.data.September2019 <- tracking.data[which(tracking.data$month=="September" & tracking.data$year=="2019"),]
previousYear(tracking.data.September2020, tracking.data.September2019)
```

### Top Releases

Most-used releases this month (including content released before this month).

```{r September 2020 Top 5 Releases, echo = FALSE, warning=FALSE, message=FALSE}
rankedreleases.September2020 <- rankReleases(tracking.data.September2020)
top10releases.September2020 <-rankedreleases.September2020[c(1:10),]
names(top10releases.September2020) <- c("Release", "Social", "Stories", "TV", "Total")
top5releases.September2020 <-rankedreleases.September2020[c(1:5),]
names(top5releases.September2020) <- c("Release", "Social", "Stories", "TV", "Total")
library(DT)
datatable(top10releases.September2020, fillContainer=FALSE, options = list(scrollX="70px", scrollY="200px", pageLength = 5, dom = 'ftp'), rownames=FALSE)
```


### Hits by Region
```{r September Hits by Region, echo = FALSE, warning=FALSE, message=FALSE}
#compute hits by regions
month.hitsbyregion.September2020 <- hitsbyregion(tracking.data.September2020)
month.hitsbyregion.September2020
```

***

# August 2020

```{r August Enrollment, include=FALSE, echo = FALSE, warning=FALSE, message=FALSE}
rows <- c("Media Meteorologists","Market Penetration (%)", "Local Television Stations", "Spanish-language Meteorologists", "Journalists Receiving CMN")
values <- c(945, 92, 473, 54, 696)
enrollment <- as.data.frame(cbind(rows, values))
names(enrollment) <- c(" ", "Enrollment")
library("formattable")
formattable(enrollment)
```

```{r August setup, echo = FALSE, warning=FALSE, message=FALSE}
tracking.data.August2020 <- tracking.data[which(tracking.data$month=="August" & tracking.data$year=="2020"),]
```

### Hits by Program
```{r August Hits by Type and Program, echo = FALSE, warning=FALSE, message=FALSE}
#expanded view
library("tidyr")
expanded.hits.draft.August2020 <- hitsbyprogram(tracking.data.August2020)
expanded.hits.August2020 <- expanded.hits.draft.August2020[,c("source", "Twitter", "fb", "other",
                                  "online.article", "radio", "tv")]
#restrict data to CC, CM, CMN sources
expanded.hits.CMprograms.August2020 <- subset(expanded.hits.August2020, source=="CC"|source=="CM"|source=="CMN")
#aggregate hits according to nest program model
CMN.August2020 <- expanded.hits.CMprograms.August2020[3,2:7]
CM.August2020 <- CMN.August2020 + expanded.hits.CMprograms.August2020[2,2:7]
CC.August2020 <- CM.August2020 + expanded.hits.CMprograms.August2020[1,2:7]
aggregated.hits.CMprograms.August2020 <- rbind(CC.August2020, CM.August2020, CMN.August2020)
rownames(aggregated.hits.CMprograms.August2020) <- c("CC", "CM", "CMN")
#change column names
names(aggregated.hits.CMprograms.August2020) <- c("Twitter", "Facebook", "Other ",
                          "Online Articles", "Radio", "TV")
library("formattable")
aggregated.hits.formatted.August2020 <- formattable(aggregated.hits.CMprograms.August2020,
                                       align=c("l", "c", "c", "c", "c", "c", "c"),
                                       list(''))
aggregated.hits.formatted.August2020
```


### Comparison with Last Year
```{r August Last Year Comparison, echo = FALSE, warning=FALSE, message=FALSE}
tracking.data.August2020 <- tracking.data[which(tracking.data$month=="August" & tracking.data$year=="2020"),]
tracking.data.August2019 <- tracking.data[which(tracking.data$month=="August" & tracking.data$year=="2019"),]
previousYear(tracking.data.August2020, tracking.data.August2019)
```

### Top Releases

Most-used releases this month (including content released before this month).

```{r August 2020 Top 5 Releases, echo = FALSE, warning=FALSE, message=FALSE}
rankedreleases.August2020 <- rankReleases(tracking.data.August2020)
top10releases.August2020 <-rankedreleases.August2020[c(1:10),]
names(top10releases.August2020) <- c("Release", "Social", "Stories", "TV", "Total")
top5releases.August2020 <-rankedreleases.August2020[c(1:5),]
names(top5releases.August2020) <- c("Release", "Social", "Stories", "TV", "Total")
library(DT)
datatable(top10releases.August2020, fillContainer=FALSE, options = list(scrollX="70px", scrollY="200px", pageLength = 5, dom = 'ftp'), rownames=FALSE)
```

### Hits by Region
```{r August Hits By Region, echo = FALSE, warning=FALSE, message=FALSE}
#compute hits by regions
month.hitsbyregion.August2020 <- hitsbyregion(tracking.data.August2020)
month.hitsbyregion.August2020$TV <- round(month.hitsbyregion.August2020$TV, digits=0)
month.hitsbyregion.August2020$Total <- round(month.hitsbyregion.August2020$Total, digits=0)
month.hitsbyregion.August2020
```

***
