---
title: "Climate Matters Monthly Numbers: August 2020"
output: html_document

---

Dashboard
===================================== 

"Social Media" includes Twitter, Facebook, Other social media, and Youtube. 
"Stories" includes online articles, radio and podcasts. 
For now, "Regions" are the same as those defined by the 2018 National Climate Assessment.


```{r eval=FALSE}
library('flexdashboard')
#source("/Users/lsheridan/Documents/R_data/releases_and_graphics/monthly_reports/montlyreport.functions.R")
#load script with functions saved
source("monthlyreport_functions.R")

#read and format dataset
library('googlesheets4')

#data <- read_sheet("https://docs.google.com/spreadsheets/d/1OdmkPrplKPKEQ7yKaRJg1ccODx05DehXftfPmWzQrWs/edit#gid=119899987", sheet=2)

#parsing data pulled from master sheet
tracking.data <-reformat_googlesheet(data)

# CHOOSE MONTH TO SUBSET
tracking.data.month <- tracking.data[which(tracking.data$month=="September" & tracking.data$year=="2020"),]
```

```{r setup}
library('flexdashboard')
source("monthlyreport_functions.R")
data <- read.csv('September2020trackingdata.csv')
tracking.data <-reformat_googlesheet(data)
tracking.data.month <- tracking.data[which(tracking.data$month=="September" & tracking.data$year=="2020"),]
```


Row {data-width=200}
-----------------------------------------------------------------------

### New CM Subscribers

```{r}
valueBox(0, caption="New CM Subscribers", icon="fa-user-friends", color="rgb(0, 131, 185)")
```

### Year-to-Date TV spots

```{r}
#don't forget to add the 20%
valueBox(0, caption="Year-to-Date TV spots", icon="fa-tv", color="rgb(73, 156, 193)")
```

Row {data-width=250 .tabset .tabset-fade}
-----------------------------------------------------------------------

### Hits by Program (Expanded View)
```{r, Hits by Type and Program, echo=FALSE}
#expanded view
library("tidyr")
expanded.hits.draft <- hitsbyprogram(tracking.data.month)
expanded.hits <- expanded.hits.draft[,c("source", "Twitter", "fb", "other",
                                  "online.article", "radio", "tv")]
names(expanded.hits) <- c("Program", "Twitter", "Facebook", "Other ",
                          "Online Articles", "Radio", "TV")
#restrict data to CC, CM, CMN sources
expanded.hits.CMprograms <- subset(expanded.hits, Program=="CC"|Program=="CM"|Program=="CMN"|Program=="Total")
library("formattable")
expanded.hits.formatted <- formattable(expanded.hits.CMprograms,
                                       align=c("l", "c", "c", "c", "c", "c", "c"),
                                       list(''))
expanded.hits.formatted
```

### (Condensed View)
```{r}
#condensed view
condensed.hits.draft <- expanded.hits.draft %>%
  as_tibble() %>%
  mutate(
    social=rt+tw+fb+other,
    stories=online.article+radio
  )
condensed.hits <- condensed.hits.draft[,c("source", "social", "stories", "tv")]
names(condensed.hits) <- c("Program", "Social Media", "Stories", "TV")

#restrict data to CC, CM, CMN sources
condensed.hits.CMprograms <- subset(condensed.hits, Program=="CC"|Program=="CM"|Program=="CMN"|Program=="Total")

#design into publishable table
library(formattable)
condensed.hits.formatted <- formattable(condensed.hits.CMprograms,align=c("l", "c", "c", "c"))

condensed.hits.formatted
```

Row {data-width=550}
-----------------------------------------------------------------------

```{r eval=FALSE}
### Most Popular Assets this Month
#What were the most popular releases this month?
top10.releases <- releases.popularity(tracking.data.month)

#What were the most popular graphics this month?
top10.graphics <- graphics.popularity(tracking.data.month)

top10.releases
top10.graphics
```

### Hits by Region
```{r}
#compute hits by regions
month.hitsbyregion <- hitsbyregion(tracking.data.month)

month.hitsbyregion
```

### Heat Map of TV Coverage
```{r}
library('usmap')
library('ggplot2')
tvheatmap.withAJFox <- tvheatmap.withAJFox(tracking.data.month)
tvheatmap.withoutAJFox <- tvheatmap.withoutAJFox(tracking.data.month)

tvheatmap.withAJFox
tvheatmap.withoutAJFox
```

CM/N in Action
===================================== 

Enter blurbs about and links to cool examples of month's hits.

Year-to-Date
=====================================

### Year-to-Date TV Airings
```{r echo=FALSE}
  #subset 2020 data
  data2020 <-tracking.data[which(tracking.data$year=="2020"),]
  #replace NAs in tv column with 0s
  data2020$tv[is.na(data2020$tv)] <- 0
  #summarize tv by month
  library("dplyr")
  tvbymonth <- data2020 %>%
    group_by(month) %>%
    summarise(tv=sum(tv))
  #add 20% to tv
  tvbymonth$tv <- tvbymonth$tv*1.2
  #order data by month
  library("dplyr")
  tvbymonth$month <- factor(tvbymonth$month, levels=month.name)
  #c("January", "February", "March", "April", "May", "June", "July", "August", "September", "October", "November", "December")
  library("tidyverse")
  tvbymonth$month <- sort(tvbymonth$month)
  #add column for cumulative sum of tv airings
  tvbymonth$cumulative.tv <- cumsum(tvbymonth$tv)
  tvbymonth <- as.data.frame(tvbymonth)
  #tv goals
  tv.goals <- c(500, 1000, 1500, 2000, 2500, 3000, 3500, 4000, 4500, 5000, 5500, 6000)
  month <- month.name
  tvgoals.bymonth <- data.frame(month, tv.goals)
  #merge hits and goals
  tvgoalsandhits <- merge(tvbymonth, tvgoals.bymonth, by="month", all.y = TRUE)
  #remove tv column
  tvgoalsandhits <- subset(tvgoalsandhits, select=-tv)
  #reorder columns
  tvgoalsandhits <- tvgoalsandhits[,c(1,3,2)]
  #melt dataframe
  library("reshape2")
  melted.tvgoalsandhits <- melt(tvgoalsandhits)
  #make variable a factor
  melted.tvgoalsandhits$variable <- factor(melted.tvgoalsandhits$variable, levels = c("tv.goals", "cumulative.tv"))
  melted.tvgoalsandhits$variable <- sort(melted.tvgoalsandhits$variable)
  #plot chart
  library("ggplot2")
  tvgoalschart <- ggplot(melted.tvgoalsandhits, aes(month, value, group=variable)) + 
    theme(axis.text.x = element_text(angle=45, vjust=0.7)) +
    geom_line(aes(color=variable)) +
    labs(y="TV Airings", x="") +
    scale_fill_discrete(name="", labels=c("Goals", "Cumulative Airings"))
  
  tvgoalschart
```

### Year-to-Date Online Articles

! Under Development !
```{r, eval=FALSE}
#subset 2020 data
data2020 <-tracking.data[which(tracking.data$year=="2020"),]



#compute hits by program
yearhitsbyprogram <- hitsbyprogram(data2020)
#restrict data to CC, CM, CMN sources
year.hits.CMprograms <- subset(yearhitsbyprogram, source=="CC"|source=="CM"|source=="CMN")
#subset print/digital
year.printdigital <- year.hits.CMprograms[,c("source", "online.article")]
```